hbm_paper_results

### 2024-05-24 paper_replication_results.Rmd
figs

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
if(!require('pacman')) {
  install.packages('pacman')
}
pacman::p_load(data.table, ggplot2, tidyverse, ggseg, ggsegExtra, paletteer, ggpubr, gridExtra, lemon, parallel, rstatix, lme4, interactions, ggrepel, ggrain, gdata)
#Sys.setenv("MC_CORES"=10L)
options("mc.cores")

@@

cent.feat.t.test.df %>%
  group_by(comp, smaller_group) %>%
  summarize(n_sig=sum(sig_fdr))
```

**need to prettify table for supplement**

@@

dataset_names <- c(ukb_CN = "Raw Data", cf = "ComBat w/o Covar", cf.lm = "ComBat", cf.gam ="ComBat-GAM", cf.gamlss ="ComBatLS")

cent.test.comp.plt <- cent.feat.t.test.df %>%
  dplyr::filter(sig_fdr==TRUE) %>%
  mutate(smaller_group=factor(smaller_group, levels=c("cf", "cf.lm", "cf.gam", "cf.gamlss"), ordered=TRUE)) %>%
ggplot() +
  geom_bar(aes(x=perm, fill=smaller_group)) +
  theme_linedraw()+
  theme(axis.text.x = element_blank()) +
  facet_grid(pheno_cat~comp, scales="free_y", labeller = labeller(comp = as_labeller(comp_names))) +
  scale_fill_manual(values = c(cf= "#440D54", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "Better ComBat \nConfiguration", labels=dataset_names) +
  labs(x="Sampling Permutation", y="Feature Count")
ggsave(paste0(base_path, "/figs/perm_cent_test_barplt.jpg"), plot=cent.test.comp.plt, width=15.5, height=6, units="in")
```

```{r}
#look at combatGAM vs combatLS
cent.feat.t.test.df %>%
  dplyr::filter(sig_fdr==TRUE & comp =="cf.gamlss_cf.gam") %>%
ggplot(aes(x=perm, fill=bigger_group)) +
  geom_bar() +
  # geom_text(stat='count', aes(label=..count..)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  facet_wrap(~pheno_cat)

cf.gam_worse <- cent.feat.t.test.df %>%
  dplyr::filter(sig_fdr==TRUE & comp =="cf.gamlss_cf.gam" & bigger_group == "cf.gamlss") %>%
  group_by(perm) %>%
  summarise(count = n())

mean(cf.gam_worse$count)
IQR(cf.gam_worse$count)
```

@@

```{r}
ct.t.tests <- cent.feat.t.test.df %>%
  dplyr::filter(comp =="cf.gamlss_cf.gam" & stringr::str_detect(pheno, "CT")) %>%
  mutate(label=gsub("_CT", "", pheno),
         better_fit = case_when(sig_fdr==TRUE & bigger_group == "cf.gam" ~ "cf.gamlss",
                              sig_fdr==TRUE & bigger_group == "cf.gamlss" ~ "cf.gam",
                              sig_fdr==FALSE ~ "NS"))

@@

ct.brain.plt <- ct.t.tests_to_plt %>%
  ggplot() +
  theme_linedraw(base_size=12) +
  ggseg::geom_brain(atlas = dk_nomed, 
             position = position_brain(hemi ~ side),
            aes(fill=better_fit)) +
  theme(axis.title = element_blank(), axis.text = element_blank(), axis.ticks = element_blank(), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.border = element_rect(color= "gray", fill = NA), aspect.ratio=, plot.margin = margin(1,1,1,1, 'pt'), strip.text.y = element_blank(),
        legend.position="top") +
  scale_fill_manual(values = c(NS= "darkgray", cf.gam = "#3D75C2", cf.gamlss ="#CFB023FF"), name = "Better ComBat Method", labels=dataset_names) +
  facet_wrap(~perm, nrow=2)

ct.t.tests_to_plt.sum <- ct.t.tests_to_plt %>%
  group_by(hemi, region, label, bigger_group) %>%
  summarise(n_worse = sum(sig_fdr)) %>%
  pivot_wider(id_cols=c(hemi, label, region), names_from = bigger_group, values_from=n_worse) %>%
  mutate(cf.gamlss=ifelse(is.na(cf.gamlss), 0, cf.gamlss)) %>%
  mutate(cf.gamlss_minus_cf.gam_better=as.integer(cf.gam-cf.gamlss),
         percent_cf.gamlss_better=(cf.gam/100)*100) %>%
  ungroup()

ct.brain.sum.plt <- ct.t.tests_to_plt.sum %>%
  ggplot() +
  theme_linedraw(base_size=12) +
  ggseg::geom_brain(atlas = dk_nomed, 
             position = position_brain(hemi ~ side),
            aes(fill=percent_cf.gamlss_better))  +
  theme(axis.title = element_blank(), axis.text = element_blank(), axis.ticks = element_blank(), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.border = element_rect(color= "gray", fill = NA), aspect.ratio=, plot.margin = margin(1,1,1,1, 'pt'), strip.text.y = element_blank()) +
  scale_fill_gradient(low="#605210", high= "#e6d16d",  name = "% Replications") +
  labs(title="Replications where ComBatLS recapitulates cortical thickness centiles \nsignificantly better than ComBat-GAM")
```

@@

@@

#look by feature type
cent.subj.sex.test.df %>%
  dplyr::filter(dataset == "cf.gam" | dataset == "cf.gamlss" | dataset == "cf.lm") %>%
  mutate(dataset = factor(dataset, levels = c("cf.lm", "cf.gam", "cf.gamlss"), ordered = TRUE)) %>%
  mutate(pheno_cat = factor(case_when(
    pheno %in% vol_list_global ~ "Global Volume",
    pheno %in% vol_list_regions ~ "Regional Volume",
    pheno %in% sa_list ~ "Regional SA",
    pheno %in% ct_list ~ "Regional CT",
    TRUE ~ NA_character_)),
    perm = as.factor(sub("perm-0", "", perm))) %>%
ggplot() +
  geom_histogram(aes(x=median_sex_diff, color=perm, fill=perm), alpha=0.3, position="identity") +
  geom_vline(xintercept = 0, linetype="dashed") +
  facet_grid(pheno_cat~dataset, scales="free", labeller = labeller(dataset = as_labeller(dataset_names))) +
  theme_linedraw(base_size=12) +
  theme(legend.position = "none") +
  labs(x="Male - Female Median Centile Errors", y="Number of Features") 
```

@@

t.test.cent.sex.test.med <- cent.sex.test.med %>%
  group_by(dataset, pheno_cat) %>%
  summarise(t.test.p = tidy(t.test(median_of_median_sex_diff))$p.value,
            t.test.est = tidy(t.test(median_of_median_sex_diff))$estimate,
            x_pos = median(median_of_median_sex_diff)) %>% #test median of each distribution against 0
  mutate(p.val_fdr = p.adjust(t.test.p, method="fdr", n = length(unique(cent.sex.test.med$dataset))*length(unique(cent.sex.test.med$pheno_cat))),
                  sig_fdr = case_when(p.val_fdr < 0.001 ~ "***",
                               p.val_fdr >= 0.001 & p.val_fdr < 0.01 ~ "**",
                               p.val_fdr >= 0.01 & p.val_fdr < 0.05 ~ "*",
                               p.val_fdr >= 0.05 ~ ""))

t.test.cent.sex.test.med.filt <- t.test.cent.sex.test.med %>% dplyr::filter(dataset == "cf.gam" | dataset == "cf.gamlss")

@@

sex_bias_density_plt <- cent.sex.test.med %>%
  dplyr::filter(dataset == "cf.gam" | dataset == "cf.gamlss") %>%
  ggplot() +
  geom_density(aes(x=median_of_median_sex_diff*100, fill=dataset, color=dataset), alpha=0.6, position = "identity") +
  geom_vline(xintercept = 0, linetype="dashed", color="#3F3F3F") +
  facet_wrap(~pheno_cat) +
  theme_linedraw() +
  geom_text(aes(label = sig_fdr, x= x_pos*100, y=ifelse(t.test.cent.sex.test.med.filt$dataset == "cf.gam", 10.2, 5.5)),
              data = t.test.cent.sex.test.med.filt) +
  scale_fill_manual(values = c(cf= "#440D54", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "ComBat \nConfiguration", labels=dataset_names) +
  scale_color_manual(values = c(cf= "#440D54", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "ComBat \nConfiguration", labels=dataset_names) +
  theme(legend.position = "bottom")+
  labs(x="Medians of Sex-Differences in Centile Errors", y="Density Across 100 Replications")

cent.sex.test.med %>%
  #dplyr::filter(dataset == "cf.gam" | dataset == "cf.gamlss") %>%
  ggplot() +
  geom_density(aes(x=median_of_median_sex_diff*100, fill=dataset, color=dataset), alpha=0.6, position = "identity") +
  geom_vline(xintercept = 0, linetype="dashed", color="#3F3F3F") +
  facet_wrap(~pheno_cat) +
  theme_linedraw() +
  geom_text(aes(label = sig_fdr, x= x_pos*100, y=ifelse(t.test.cent.sex.test.med$dataset == "cf.gam", 10.2, 5.5)),
              data = t.test.cent.sex.test.med) +
  scale_fill_manual(values = c(cf= "#440D54", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "ComBat \nConfiguration", labels=dataset_names) +
  scale_color_manual(values = c(cf= "#440D54", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "ComBat \nConfiguration", labels=dataset_names) +
  theme(legend.position = "bottom")+
  labs(x="Medians of Sex-Differences in Centile Errors", y="Density Across 100 Replications")
```

@@

@@

all_cent_sum_boxplt <- all_cent_sum.df %>%
  dplyr::filter(dataset != "raw" & dataset != "cf") %>%
  mutate(source = factor(source, levels=c("low", "high", "ext"), ordered=TRUE)) %>%
  ggplot(aes(x=dataset, y=female_ratio)) +
  geom_boxplot(aes(color=dataset)) +
  # geom_dotplot(binaxis = "y", stackdir="center") +
  facet_grid(pheno_cat~source, scales="free_y", labeller = labeller(source=cent_ext_list)) +
  geom_hline(data=all_cent.sum_raw, aes(yintercept=female_ratio), linetype="dashed")+
  # geom_text(aes(label = sig_fdr, y = max_val + 0.01),
  #             data = all_t_test.df[which(all_t_test.df$dataset != "cf"),]) +
  scale_color_manual(values = c(cf= "#440D54", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF")) + 
  theme_linedraw() +
  scale_x_discrete(labels=dataset_names) +
  # scale_y_continuous(labels=function(x)x/all_t_test.df$female_ratio[which(raw_df$pheno_cat == pheno_cat)]) + 
  theme(legend.position="none", plot.title = element_text(size=12), axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(y="Proportion Female", x = "Dataset")

all_cent_sum.df_scaled %>%
  dplyr::filter(dataset != "raw" & dataset != "cf") %>%
  mutate(source = factor(source, levels=c("low", "high", "ext"), ordered=TRUE)) %>%
  ggplot(aes(x=dataset, y=female_ratio_sc)) +
  geom_boxplot(aes(color=dataset)) +
  # geom_dotplot(binaxis = "y", stackdir="center") +
  facet_grid(pheno_cat~source, scales="free_y", labeller = labeller(source=cent_ext_list)) +
  geom_hline(yintercept=1, linetype="dashed")+
  # geom_text(aes(label = sig_fdr, y = max_val + 0.01),
  #             data = all_t_test.df[which(all_t_test.df$dataset != "cf"),]) +
  scale_color_manual(values = c(cf= "#440D54", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF")) + 
  theme_linedraw() +
  scale_x_discrete(labels=dataset_names) +
  # scale_y_continuous(labels=function(x)x/all_t_test.df$female_ratio[which(raw_df$pheno_cat == pheno_cat)]) + 
  theme(legend.position="none", plot.title = element_text(size=12), axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(y="Female Bias", x = "Dataset")

all_cent_sum_boxplt.diff <- all_cent_sum.df_scaled %>%
  dplyr::filter(dataset != "raw" & dataset != "cf") %>%
  mutate(source = factor(source, levels=c("low", "high", "ext"), ordered=TRUE)) %>%
  ggplot(aes(x=dataset, y=female_ratio_diff)) +
  geom_boxplot(aes(color=dataset)) +
  # geom_dotplot(binaxis = "y", stackdir="center") +
  facet_grid(pheno_cat~source, scales="free_y", labeller = labeller(source=cent_ext_list)) +
  geom_hline(yintercept=0, linetype="dashed")+
  # geom_text(aes(label = sig_fdr, y = max_val + 0.01),
  #             data = all_t_test.df[which(all_t_test.df$dataset != "cf"),]) +
  scale_color_manual(values = c(cf= "#440D54", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF")) + 
  theme_linedraw() +
  scale_x_discrete(labels=dataset_names) +
  # scale_y_continuous(labels=function(x)x/all_t_test.df$female_ratio[which(raw_df$pheno_cat == pheno_cat)]) + 
  theme(legend.position="none", plot.title = element_text(size=12), axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(y="Female Bias", x = "Dataset")

@@

linear ComBat ~ too few women with high centiles, too many women with low centiles; ~ balances out overall

ComBat-GAM -> variable pattern, pretty close to raw

ComBatLS -> pretty close to raw!

@@

look at combatGAM vs combatLS

```{r}
z.feat.t.test.df %>%
  dplyr::filter(sig_fdr==TRUE & comp =="cf.gamlss_cf.gam") %>%
ggplot(aes(x=perm, fill=bigger_group)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  facet_wrap(~pheno_cat)

z.feat.t.test.df %>%
  dplyr::filter(sig_fdr==TRUE & comp =="cf.gamlss_cf.gam") %>%
ggplot(aes(x=perm, fill=bigger_group)) +
  geom_bar(position='fill') +
  geom_hline(yintercept = .5) +
  theme(axis.text.x = element_blank()) +
  facet_wrap(~pheno_cat)
```

@@

## Supplemental Fig
```{r}
sfig <- ggarrange(cent.test.comp.plt, ct.brain.sum.plt,
                  ncol=1, nrow=2, heights = c(2, 1))
sfig
ggsave(paste0(base_path, "/figs/combat_abs_errs_supp_plt.jpg"), plot=sfig, width=11, height=7, units="in")

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
if(!require('pacman')) {
  install.packages('pacman')
}
pacman::p_load(data.table, ggplot2, tidyverse, ggseg, ggsegExtra, paletteer, ggpubr, gridExtra, lemon, parallel, rstatix, lme4, interactions, ggrepel, ggrain, gdata, gtExtras)
#Sys.setenv("MC_CORES"=10L)
options("mc.cores")

@@

cent.tbl <- cent.feat.t.test.df %>%
  group_by(comp, smaller_group) %>%
  summarize(n_sig=sum(sig_fdr)) %>%
  mutate(perc_tests = n_sig/(208*100))

cent.tbl.pretty <- cent.tbl %>%
  mutate(comp = case_when(comp == "cf.gam_cf" ~ "ComBat-GAM vs ComBat w/o Covariates",
                          comp == "cf.gamlss_cf" ~ "ComBatLS vs ComBat w/o Covariates", 
                          comp == "cf.gamlss_cf.gam" ~ "ComBatLS vs ComBat-GAM",
                          comp == "cf.lm_cf" ~ "Linear ComBat vs ComBat w/o Covariates",
                          comp == "cf.lm_cf.gam" ~ "Linear ComBat vs ComBat-GAM",
                          comp == "cf.lm_cf.gamlss" ~ "Linear ComBat vs ComBatLS"),
         smaller_group = case_when(smaller_group == "cf" ~ "ComBat w/o Covariates",
                                   smaller_group == "cf.lm" ~ "Linear ComBat",
                                   smaller_group == "cf.gam" ~ "ComBat-GAM",
                                   smaller_group == "cf.gamlss" ~ "ComBatLS")) %>%
  rename(#"Pairwise Comparison"=comp,
         "Lower Errors" = smaller_group,
         "N Features" = n_sig,
         "% Features" = perc_tests)

cent.tbl.pretty %>%
  gt() %>% 
  #gt_theme_538() %>% 
tab_style(style = list(cell_fill(color = "gray95")),
    locations = cells_row_groups()) %>%
  fmt_percent(
    columns = "% Features",
    decimals = 2
  ) %>%
  tab_options(column_labels.font.weight = "bold") %>%
  tab_header(title = "Pairwise comparisons of ComBat methods' absolute centile errors for 208 brain features across 100 replications")
```

@@

dataset_names <- c(raw = "Raw Data", cf = "ComBat w/o Covar", cf.lm = "ComBat", cf.gam ="ComBat-GAM", cf.gamlss ="ComBatLS")

cent.test.comp.plt <- cent.feat.t.test.df %>%
  dplyr::filter(sig_fdr==TRUE) %>%
  mutate(smaller_group=factor(smaller_group, levels=c("cf", "cf.lm", "cf.gam", "cf.gamlss"), ordered=TRUE)) %>%
ggplot() +
  geom_bar(aes(x=perm, fill=smaller_group)) +
  theme_linedraw()+
  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank(), legend.position = "bottom") +
  facet_grid(pheno_cat~comp, scales="free_y", labeller = labeller(comp = as_labeller(comp_names))) +
  scale_fill_manual(values = c(cf= "#440D54", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "Better ComBat \nConfiguration", labels=dataset_names) +
  labs(x="Sampling Permutation", y="Feature Count")
```

```{r}
cent.feat.t.test.df %>%
  dplyr::filter(bigger_group=="cf.gamlss" & sig_fdr==TRUE) %>%
  group_by(comp, pheno_cat) %>%
  summarize(count = n())

cent.feat.t.test.df %>%
  dplyr::filter(sig_fdr==TRUE & bigger_group == "cf.gamlss") %>%
  group_by(comp, perm) %>%
  summarise(count = n()) %>%
  ungroup() %>%
  group_by(comp) %>%
  summarize(med.count = median(count),
            IQR.count = IQR(count))
```

@@

```{r}
ct.t.tests <- cent.feat.t.test.df %>%
  dplyr::filter(pheno_cat == "Regional CT" & grepl("gamlss", comp)) %>%
  mutate(label=gsub("_CT", "", pheno))

@@

ct.t.tests_to_plt.sum <- ct.t.tests_to_plt %>%
  group_by(comp, hemi, region, label, smaller_group) %>%
  summarise(n_better = sum(sig_fdr)) %>%
  mutate(perc.better=n_better/100) %>% #make NAs into 0s
  ungroup() %>%
  pivot_wider(id_cols=c(comp, hemi, label, region), names_from = smaller_group, values_from=perc.better) %>%
  dplyr::select(!c(cf, cf.lm, cf.gam))

min(ct.t.tests_to_plt.sum$cf.gamlss)

comp_names <- c(cf.gamlss_cf = "vs. ComBat w/o Covar", cf.lm_cf.gamlss = "vs. linear ComBat", cf.gamlss_cf.gam ="vs. ComBat-GAM")

ct.brain.sum.plt <- ct.t.tests_to_plt.sum %>%
  mutate(comp=as.character(comp)) %>%
  ggplot() +
  theme_linedraw(base_size=12) +
  ggseg::geom_brain(atlas = dk_nomed, 
             position = position_brain(hemi ~ side),
            aes(fill=cf.gamlss))  +
  theme(axis.title = element_blank(), axis.text = element_blank(), axis.ticks = element_blank(), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.border = element_rect(color= "gray", fill = NA), aspect.ratio=, plot.margin = margin(1,1,1,1, 'pt'), strip.text.y = element_blank()) +
  scale_fill_gradient(low="#605210", high= "#EFE2A2",  name = "Proportion Replications", limits = c(.5, 1), breaks=c(0.50, 0.75, 1.00)) +
  facet_wrap(~comp, labeller = labeller(comp = as_labeller(comp_names)))
ct.brain.sum.plt
```

@@

simple bar-plot to count regions w significant sex-biases

@@

#look by feature type
sex_bias_hist_plt <- cent.subj.sex.test.df %>%
  dplyr::filter(dataset == "cf.gam" | dataset == "cf.gamlss" | dataset == "cf.lm") %>%
  mutate(dataset = factor(dataset, levels = c("cf.lm", "cf.gam", "cf.gamlss"), ordered = TRUE)) %>%
  mutate(pheno_cat = factor(case_when(
    pheno %in% vol_list_global ~ "Global Volume",
    pheno %in% vol_list_regions ~ "Regional Volume",
    pheno %in% sa_list ~ "Regional SA",
    pheno %in% ct_list ~ "Regional CT",
    TRUE ~ NA_character_)),
    perm = as.factor(sub("perm-0", "", perm))) %>%
ggplot() +
  geom_histogram(aes(x=median_sex_diff, color=perm, fill=perm), alpha=0.3, position="identity", bins=40) +
  geom_vline(xintercept = 0, linetype="dashed") +
  facet_grid(pheno_cat~dataset, scales="free_y", labeller = labeller(dataset = as_labeller(dataset_names))) +
  theme_linedraw(base_size=12) +
  theme(legend.position = "none") +
  labs(x="Male - Female Median Centile Errors", y="Number of Features") +
  ggtitle("Sex differences in median centile errors across 100 sampling replications")
ggsave(filename="figs/sex_bias_hist_plt.png", sex_bias_hist_plt)
```

@@

t.test.cent.sex.test.med <- cent.sex.test.med %>%
  group_by(dataset, pheno_cat) %>%
  summarise(t.test.p = tidy(t.test(median_of_median_sex_diff))$p.value,
            t.test.est = tidy(t.test(median_of_median_sex_diff))$estimate,
            x_pos = median(median_of_median_sex_diff)) %>% #test median of each distribution against 0
  mutate(p.val_fdr = p.adjust(t.test.p, method="fdr", n = length(unique(cent.sex.test.med$dataset))*length(unique(cent.sex.test.med$pheno_cat))),
                  sig_fdr = case_when(p.val_fdr < 0.001 ~ "***",
                               p.val_fdr >= 0.001 & p.val_fdr < 0.01 ~ "**",
                               p.val_fdr >= 0.01 & p.val_fdr < 0.05 ~ "*",
                               p.val_fdr >= 0.05 ~ ""),
         y_pos = case_when(dataset=="cf" ~ 11,
                           dataset=="cf.lm" ~ 11,
                           dataset=="cf.gam" ~ 10.5,
                           dataset=="cf.gamlss" ~ 6))

@@

t.test.cent.sex.test.med.filt <- t.test.cent.sex.test.med %>% dplyr::filter(dataset != "cf")

sex_bias_density_plt <- cent.sex.test.med %>%
  dplyr::filter(dataset != "cf") %>%
  ggplot() +
  geom_density(aes(x=median_of_median_sex_diff*100, fill=dataset, color=dataset), alpha=0.6, position = "identity") +
  geom_vline(xintercept = 0, linetype="dashed", color="#3F3F3F") +
  facet_wrap(~pheno_cat) +
  theme_linedraw() +
  geom_text(aes(label = sig_fdr, x= x_pos*100, y=y_pos),
              data = t.test.cent.sex.test.med.filt) +
  scale_fill_manual(values = c(cf= "#440D54", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "ComBat \nConfiguration", labels=dataset_names) +
  scale_color_manual(values = c(cf= "#440D54", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "ComBat \nConfiguration", labels=dataset_names) +
  theme(legend.position = "bottom")+
  labs(x="Medians of Sex-Differences in Centile Errors", y="Density Across 100 Replications")
```

@@

y_pos.df <- all_cent_sum.df_scaled %>%
  group_by(source, pheno_cat, dataset) %>%
  summarise(y_pos=max(female_ratio_diff))

all_t_test.df <- full_join(all_t_test.df, y_pos.df)

@@

all_cent_sum_boxplt.diff <- all_cent_sum.df_scaled %>%
  dplyr::filter(dataset != "raw" & dataset != "cf" & source != "ext") %>%
  mutate(source = factor(source, levels=c("low", "high", "ext"), ordered=TRUE)) %>%
  ggplot(aes(x=dataset, y=female_ratio_diff)) +
  geom_boxplot(aes(color=dataset)) +
  # geom_dotplot(binaxis = "y", stackdir="center") +
  facet_grid(pheno_cat~source, scales="free_y", labeller = labeller(source=cent_ext_list)) +
  geom_hline(yintercept=0, linetype="dashed")+
  geom_text(aes(label = sig_fdr, y = (y_pos)), nudge_y=.005,
               data = all_t_test.df[which(all_t_test.df$dataset != "cf" & all_t_test.df$source != "ext"),]) +
  scale_color_manual(values = c(cf= "#440D54", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF")) + 
  theme_linedraw() +
  scale_x_discrete(labels=dataset_names) +
  # scale_y_continuous(labels=function(x)x/all_t_test.df$female_ratio[which(raw_df$pheno_cat == pheno_cat)]) + 
  theme(legend.position="none", plot.title = element_text(size=12), axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(y="Female Bias", x = "Dataset")

@@

@@

look at ratios
```{r}
z.feat.t.test.df %>%
  dplyr::filter(sig_fdr==TRUE & grepl("gamlss", comp)) %>%
ggplot(aes(x=perm, fill=bigger_group)) +
  geom_bar(position='fill') +
  geom_hline(yintercept = .5) +
  theme(axis.text.x = element_blank()) +
  facet_grid(comp~pheno_cat)
```

@@

## Supplemental Fig
```{r}
sfig <- ggarrange(cent.test.comp.plt, ct.brain.sum.plt,
                  ncol=1, nrow=2, heights = c(1.8, 1), labels = "AUTO")
sfig
ggsave(paste0(base_path, "/figs/combat_abs_errs_supp_plt.jpg"), plot=sfig, width=13, height=9, units="in")
```
